\section{Preliminary 'Table of contents'}
What follows is a guess as to how the table of contents of the final report might look. This is provided to illustrate what the focus of the project is thought to be, and to provide a starting point for the actual report.
\begin{itemize}
  \item \textbf{Description of the problem}
  \begin{itemize}
    \item \textbf{Background}\\A section on the medical background of the problem, much like the one in this synopsis but likely improved with relevant details
    \item \textbf{Mathematical model}\\A description of the mathematical modelling of the scan, though to resemble the one in this synopsis.
    \item \textbf{A formal problem description}\\Here a formal problem description is made, so that its abundantly clear what the focus of the project is.
    \item \textbf{A remark on alternate methods}\\A section on other know methods of solving this kind of problem. Namely \emph{Filtered back projection}.
  \end{itemize}
  \item \textbf{Futhark implementation}
  \begin{itemize}
    \item \textbf{Description of the pipeline}\\This section should outline the pipeline that this projects code has to fit in. It should be made clear what sort of input the code is given, and what guaranties it should provide regarding its output.
    \item \textbf{Implementation details}\\Here the details of the implementation is provided. This section should focus on \emph{why} rather than \emph{how}.
    \item \textbf{Verification of correctness}\\The testing methodology should be outlined here. This section should focus on whether the implementation produces \emph{correct} results. Efficiency has its own section later.
  \end{itemize}
  \item \textbf{Evaluating the efficiency of the solution}
  \begin{itemize}
    \item \textbf{Benchmarking}\\It should be described how the efficiency of the implementation was tested and the results should be presented.
    \item \textbf{Optimizations}\\This section presents the optimizations that were performed on the code, by outlining critical regions of the code or showcasing specific changes.
    \item \textbf{Bottlenecks}\\Here the parts of the whole procedure that are thought (or hopefully known) to take the largest toll on efficiency are presented.
  \end{itemize}
  \item \textbf{Conclusion}
\end{itemize}
  